Molecular alignment on graphene surface determines tansport properties of graphene/organic semiconductor transistors

### 2020-04-09 manuscript.tex
Update manuscript.tex
just small corrections
model equation
added errors

A detailed study of the initial stages of growth of PDI8-CN2 on SiO$_{2}$ was studied by Liscio et al.
\cite{liscio-2013}.
 They have compared the morphology of the layers grown at 25 $^\circ$C and at 120 $^\circ$C.
 Their results show that higher substrate temperature results at higher degree of order in the layers, which at 120 $^\circ$C grow predominantly by aggregation of molecules oriented almost perpendicularly to the substrate and yielding thickness of the first monolayer of ~1.8 nm.
 At 25 $^\circ$C instead they observe morphology that is characterized by a mixture of islands formed by molecules oriented upright on the substrate and the islands formed by molecules lying flat on the substrate (observed height ~0.5 nm).
 Interestingly, despite this heterogenous growth the surface roughness of the first monolayer is the same, albeit the layer density is lower in the samples prepared at room temperature, as assessed from the oscillations of the x-ray intensity.
The observed layer thickness in our case is consistent with PDI8-CN2 molecules lying flat on the graphene substrate, since the a-axis of the PDI8-CN2 unit cell, is 0.5 nm \cite{liscio-2012}.
 We also note, that no second layer nucleation is observed although the coverage of the first monolayer is less than 70 \%.
 This is consistent with the results from Ref.
 \onlinecite{liscio-2013}, who observed the onset of nucleation of the second layer upon completion of 95 \% coverage of the first.
 The rms roughness of our layers was consistently found to be 0.5 nm.
 As the exposure to the source materials increased from 1 minute to 3 minutes.
 The layer morphology changes as illustrated in Figure \ref{fig:2}.
 Figure \ref{fig:2}a is a  3$\times$3 $\mu$m topography map and shows two broad regions.
 The brighter region on the left of the image diagonal corresponds to single-layer graphene, the region on the right is SiO$_{2}$ substrate.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig2}
  \caption{a) $3\times3 \mu$m$^{2}$ non-contact topography map of a PDI8-CN2 layer on a single-layer graphene (leftmost region of the image) and on SiO$_{2}$ (rightmost region of the image).
 The growth time was 3 minutes.
 Brighter tones represent higher elevations.
 b) The height distribution of the image shown in Figure 2a) obtained from the height data of graphene region only.
 The histogram has been normalized to the highest value in the image.
 The black dots represent the data, the green curves are Gaussian functions used to fit the data.
 The composite fit is represented by the red curve.
  The leftmost peak corresponds to the depressions in the complete layer, which is represented by the highest peak.
 The lowest peak in the model corresponds to the few islands nucleating on the second layer.
}  \label{fig:2}
\end{figure}

@@

The resistance ($R=V_{G}/I_{DS}$) plots calculated from the data used to plot Figure \ref{fig:3} are shown in Figure \ref{fig:4} where we also show the results of a least-square fitting of the data (symbols) to a model function explained in the following.
In the outset we note that the drain current was calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- 2I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 Here $n_o$ represents a carrier concentration induced by charged impurities residing within the SiO$_{2}$ and arise from the reactions on its surface\cite{adam-2007}.
 $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and the graphene/bottom gate capacitance.
The latter can be considered as sum of  the quantum capacitance -- dependent on the position of the  Fermi level ($E_F$)  in  graphene, 
 and the electrostatic  capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006}.
 For the thickness of the SiO$_{2}$ $d_{ox}=$285 nm and its dielectric constant  $\epsilon \approx 4$,  $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$.
 The quantum capacitance has been shown to be on the order of $ \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}, and can therefore be ignored in our case\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of CNP\cite{xia-2010}.
 The total resistance $R$ of the structure is the resistance of the  channel plus the resistance of the contacts and can be  obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +2 R_{C}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{C}$, $\mu$, $n_0$ and $n(V_{CNP})$.
 Their  values for the three cases considered are summarised in Table \ref{tab:1}.

@@

\noindent \begin{table}[h]
  \centering
  \begin{tabular}{|l|r|r|r|r|r|r|} \hline%
   & $n_{0}$ (cm$^{-2}$ )& $R_{c}^{h}(\Omega$) & $R_{c}^{e}(\Omega)$ & $\mu_{h}$ (cm$^{2}$/Vs) & $\mu_{e}$ (cm$^{2}$/Vs) & $V_{D}(V) $  \\ \hline%
    Clean gr.
 & 3.
33$\times 10^{11}$ & 3303 & 2469 & 26920 & 15772 & 8.0 \\
    70\% cov.
 &3.
71$\times 10^{11}$ & 2694 & 2262 & 18537 & 14474 & 8.5 \\
     100\% cov.
 &7.
42$\times 10^{11}$ & 2632 & 2548 & 3543 & 3471 & 1.0 \\ \hline

@@

Coupled to the change in the position of CNP is also an increase in the overall resistance of the structure.
 This is because for the OS layers the metallic contacts are of the  bottom-contact type, and charge transport occurs in parallel through graphene and the second layer of PDI8-CN8, in which $\pi$-stacking provides more favorable charge transporting lane than the flat-lying molecules.
 Overall resistance is therefore net resistance between graphene and PDI8-CN2.
 Interestingly the asymmetry in contact resistance for holes (R$_{h}$) and  electrons  (R$_{e}$) on clean graphene as obtained from the model is quite appreciable and reflects the qualitative arguments given above.
  On fully covered graphene, when the charge transport proceeds also over PDI8-CN2 layer for which the contacts are of the bottom-type this asymmetry almost vanishes (R$_{e}$=2632 $\Omega$, vs. R$_{h}=2548\ \Omega$).
  Coupled to the doping structure of the channel discussed above is also asymmetry in hole mobility  ($\mu_{h}= 26920$ cm$^{2}$/Vs ) and electron mobility ($\mu_{h}= 15772$ cm$^{2}$/Vs) on clean graphene.
 As the PDI8-CN2 layer is completed the mobility is drastically reduced relative to the clean graphene.
  This argues for the opening of the charge transport venue through the second layer of $\pi-\pi$ molecular array.
 Transport is ambipolar and characterized by charge carrier mobility values that are unprecedented for an OS-graphene system.

>>>>

A detailed study of the initial stages of growth of PDI8-CN2 on SiO$_{2}$ was studied by Liscio et al.
\cite{liscio-2013}.
 They have compared the morphology of the layers grown at 25 $^\circ$C and at 120 $^\circ$C.
 Their results show that higher substrate temperature results at higher degree of order in the layers, which at 120 $^\circ$C grow predominantly by aggregation of molecules oriented almost perpendicularly to the substrate and yielding thickness of the first monolayer of ~1.8 nm.
 At 25 $^\circ$C instead they observe morphology that is characterized by a mixture of islands formed by molecules oriented upright on the substrate and the islands formed by molecules lying flat on the substrate (observed height ~0.5 nm).
 Interestingly, despite this heterogenous growth the surface roughness of the first monolayer is the same, albeit the layer density is lower in the samples prepared at room temperature, as assessed from the oscillations of the x-ray intensity.
The observed layer thickness in our case is consistent with PDI8-CN2 molecules lying flat on the graphene substrate, since the a-axis of the PDI8-CN2 unit cell, is 0.5 nm \cite{liscio-2012}.
 We also note, that no second layer nucleation is observed although the coverage of the first monolayer is less than 70 \%.
 This is consistent with the results from Ref.
 \onlinecite{liscio-2013}, who observed the onset of nucleation of the second layer upon completion of 95 \% coverage of the first.
 The rms roughness of our layers was consistently found to be 0.5 nm.
 As the exposure to the source materials increased from 1 minute to 3 minutes.
 The layer morphology changes as illustrated in Figure \ref{fig:2}.
 Figure \ref{fig:2}a is a  3$\times$3 $\mu$m$^{2}$ topography map and shows two broad regions.
 The brighter region on the left of the image diagonal corresponds to single-layer graphene, the region on the right is SiO$_{2}$ substrate.

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.9\textwidth]{./Figures/fig2}
  \caption{a) $3\times3$ $\mu$m$^{2}$ non-contact topography map of a PDI8-CN2 layer on a single-layer graphene (leftmost region of the image) and on SiO$_{2}$ (rightmost region of the image).
 The growth time was 3 minutes.
 Brighter tones represent higher elevations.
 b) The height distribution of the image shown in Figure 2a) obtained from the height data of graphene region only.
 The histogram has been normalized to the highest value in the image.
 The black dots represent the data, the green curves are Gaussian functions used to fit the data.
 The composite fit is represented by the red curve.
  The leftmost peak corresponds to the depressions in the complete layer, which is represented by the highest peak.
 The lowest peak in the model corresponds to the few islands nucleating on the second layer.
}  \label{fig:2}
\end{figure}

@@

The resistance ($R=V_{G}/I_{DS}$) plots calculated from the data used to plot Figure \ref{fig:3} are shown in Figure \ref{fig:4} where we also show the results of a least-square fitting of the data (symbols) to a model function explained in the following.
In the outset we note that the drain current was calculated as:
  \begin{equation}
    \label{eq:2}
    I_{D}=\frac{W}{L}\mu n e(V_{D}- I_{D}R_{C})
  \end{equation}
  \noindent With $W$ and $L$ channel width and length respectively, $R_{C}$ the resistance of both metallic contacts, $\mu$ charge carrier mobility and $n$ their concentration.
   Given by:
  \begin{equation}
    \label{eq:3}
    n=\sqrt{n_{o}^{2}+n^{2}(V_{g})}
  \end{equation}
 Here $n_o$ represents a carrier concentration induced by charged impurities residing within the SiO$_{2}$ and arise from the reactions on its surface\cite{adam-2007}.
 $n(V_{g})$ represents surface density of charge in graphene ($n$), which depends on the gate voltage and the graphene/bottom gate capacitance.
The latter can be considered as sum of  the quantum capacitance -- dependent on the position of the  Fermi level ($E_F$)  in  graphene, 
 and the electrostatic  capacitance between the graphene layer and the gate electrode, given by $C_{ox}=(\epsilon_0\epsilon)/d_{ox}$\cite{sze-2006}.
 For the thickness of the SiO$_{2}$ $d_{ox}=$285 nm and its dielectric constant  $\epsilon \approx 3.9$,  $C_{ox}=1.2\times10^{-12}$ F cm$^{-2}$.
 The quantum capacitance has been shown to be on the order of $ \geq 8 \times10^{-7}$ F cm$^{-2}$ \cite{xia_2009}, and can therefore be ignored in our case\cite{das-2008}. 
 Therefore, the $V_{g}$-modulated carrier concentration in graphene is given by
 \begin{equation}
   \label{eq:4}
   n(V_{g})= \frac{C_{ox}}{e}(V_{g}- V_{CNP})
 \end{equation}
 \noindent With $V_{CNP}$ the gate voltage of CNP\cite{xia-2010}.
 The total resistance $R$ of the structure is the resistance of the  channel plus the resistance of the contacts and can be  obtained from (\ref{eq:2}-\ref{eq:4}):	
 \begin{equation}
	 \label{eq:5}
     R_{tot} = \frac{V_{D}}{I_{D}} = \frac{L}{W\mu e\sqrt{n_{0}^{2}+n^{2}(V_{g})}} +R_{C}
 \end{equation}
 \noindent The results of the least-square fitting of (\ref{eq:5}) to measurements are shown by black solid lines in Figure \ref{fig:4}. The fitting parameters were $R_{C}$, $\mu$, $n_0$ and $n(V_{CNP})$.
 Their  values for the three cases considered are summarised in Table \ref{tab:1}.

@@

\noindent \begin{table}[h]
  \centering
  \begin{tabular}{|l|r|r|r|r|r|r|} \hline%
   & $n_{0}$ (cm$^{-2}$ )& $R_{c}^{h}(\Omega$) & $R_{c}^{e}(\Omega)$ & $\mu_{h}$ (cm$^{2}$/Vs) & $\mu_{e}$ (cm$^{2}$/Vs) & $V_{D}(V) $  \\ \hline%
    Clean gr.
 & 3.
33$\times 10^{11}$ & 3303 $\pm$ 4 & 2469 $\pm$ 4 & 27000 $\pm$ 4000 & 16000 $\pm$ 3000 & 8.0 \\
    70\% cov.
 &3.
71$\times 10^{11}$ & 2695 $\pm$ 6 & 2262 $\pm$6 & 19000 $\pm$ 3000 & 14000 $\pm $2000 & 8.5 \\
     100\% cov.
 &7.
42$\times 10^{11}$ & 2630 $\pm$ 10 & 2550 $\pm$10 & 3500 $\pm$ 600 & 3400 $\pm$ 600 & 1.0 \\ \hline

@@

Coupled to the change in the position of CNP is also an increase in the overall resistance of the structure.
 This is because for the OS layers the metallic contacts are of the  bottom-contact type, and charge transport occurs in parallel through graphene and the second layer of PDI8-CN8, in which $\pi$-stacking provides more favorable charge transporting lane than the flat-lying molecules.
 Overall resistance is therefore net resistance between graphene and PDI8-CN2.
 Interestingly the asymmetry in contact resistance for holes (R$_{h}$) and  electrons  (R$_{e}$) on clean graphene as obtained from the model is quite appreciable and reflects the qualitative arguments given above.
  On fully covered graphene, when the charge transport proceeds also over PDI8-CN2 layer for which the contacts are of the bottom-type this asymmetry almost vanishes (R$_{e}$=2630 $\pm$ 10 $\Omega$, vs. R$_{h}$=2550 $\pm$ 10 $\Omega$).
  Coupled to the doping structure of the channel discussed above is also asymmetry in hole mobility  ($\mu_{h}$= 27000 $\pm$ 4000 cm$^{2}$/Vs ) and electron mobility ($\mu_{h}$= 16000 $\pm$ 3000 cm$^{2}$/Vs) on clean graphene.
 As the PDI8-CN2 layer is completed the mobility is drastically reduced relative to the clean graphene.
  This argues for the opening of the charge transport venue through the second layer of $\pi-\pi$ molecular array.
 Transport is ambipolar and characterized by charge carrier mobility values that are unprecedented for an OS-graphene system.
